---
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
source("common.R")
columns(1, 2 / 3)
```

# 第一步 {#getting-started}

## 引言

本章的目的是教你如何尽快使用 ggplot2 生成有用的图形。你将学习 `ggplot()` 的基础知识以及一些有用的“配方”，以制作出最重要的图表。 `ggplot()` 允许你仅用几行代码即可完成复杂的绘图，因为它基于丰富的基础理论（即图形语法）。在这里，我们将跳过理论，而将重点放在练习上，在以后的章节中，你将学习如何使用语法的全部表达能力。

在本章中，你将学习：

- 关于 ggplot2 内置的 mpg 数据集，见小节 \@ref(fuel-economy-data)。

- 每个情节的三个关键组成部分：数据（data），美学（aesthetics）和几何图形（geom），见小节 \@ref(basic-use)。

- 如何通过美学将更多变量添加到绘图中，见小节 \@ref(aesthetics)。

- 如何使用通过刻面（facet）创建的多个小技巧在绘图中显示其他类别变量，见小节 \@ref(qplot-faceting)。

- 您可以使用多种不同的几何图形来创建不同类型的绘图，见小节 \@ref(plot-geoms)。

- 如何修改轴（axes），见小节 \@ref(axes)。

- 除了显示对象外，您还可以使用绘图对象执行的操作，例如将其保存到磁盘，见小节 \@ref(output)。

## 燃油经济性数据 {#fuel-economy-data}

在本章中，我们将主要使用与 ggplot2 绑定的一个数据集：mpg 。它包含由美国环境保护署收集的有关 1999 年和 2008 年流行车型的燃油经济性的信息， <http://fueleconomy.gov>。您可以通过加载 ggplot2 来访问数据：\index{Data!mpg@\texttt{mpg}}

```{r}
library(ggplot2)
mpg
```

这里的变量大多是顾名思义的：

- `cty` 和 `hwy` 记录城市和高速公路行驶的每加仑英里数（mpg）。

- `displ` 是发动机排量（升）。

- `drv` 是传动系统：前轮（f），后轮（r）或四轮（4）。

- `model` 是汽车的模型。之所以选择 38 种型号，是因为它们在 1999 年至 2008 年之间每年都有新版本。

- `class` 是描述汽车“类型”的类别变量：两个座位，SUV，紧凑型车等。

该数据集提出了许多有趣的问题。发动机尺寸和燃油经济性如何相关？某些制造商是否比其他制造商更在意燃油经济性？在过去的十年中，燃油经济性有所改善吗？ 我们将尝试回答其中一些问题，并在此过程中学习如何使用 ggplot2 创建一些基本图。

### 练习题

1.  列出五个函数，您可以使用这些函数来获取有关 mpg 数据集的更多信息。

2.  您如何找出 ggplot2 还包含哪些其他数据集？

3.  除美国外，大多数国家/地区使用的是油耗（固定距离内消耗的燃油），而不是燃油经济性（固定量的燃油所行驶的距离）。 您如何将 `cty` 和 `hwy` 转换为 l / 100km 的欧洲标准？

4.  哪个制造商在该数据集中拥有最多的模型？ 哪个型号变化最大？如果从型号名称中删除了传动系统的冗余规格（例如“pathfinder 4wd”，“a4 quattro”），答案会有所变化吗？

## 关键组件 {#basic-use}

每个 ggplot2 图都有三个关键组成部分：

1.**数据**, 

2.  数据和视觉属性之间的一组**美学映射**

3.  至少一层描述如何呈现每个观察值。通常使用 `geom` 函数创建图层。

这里有一个简单的例子： \index{Scatterplot} \indexf{ggplot}

```{r qscatter}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point()
```

这将产生一个散点图，其定义为：

1.  数据：mpg。
2.  美学映射：发动机尺寸映射到 `x` 位置，燃油经济性映射到 `y` 位置。
3.  层数：分。

注意此函数调用的结构： `ggplot()` 中提供了数据和美学映射，然后将图层添加到 `+` 上。 这是一种重要的模式，随着您对 ggplot2 的更多了解，您将通过添加更多类型的组件来构建越来越复杂的图。

几乎每个图都将变量映射到 `x` 和 `y` ，因此命名这些美学是乏味的，因此， `aes()` 的前两个未命名参数将被映射为 `x` 和 `y` 。这意味着以下代码与上面的示例相同：

```{r, eval = FALSE}
ggplot(mpg, aes(displ, hwy)) +
  geom_point()
```

在整本书中，我都会坚持这种风格，因此，请不要忘记 `aes()` 的前两个参数是 x 和 y。请注意，我已将每个命令放在新行上。我建议您在自己的代码中执行此操作，因此可以轻松扫描绘图说明并准确查看其中的内容。在本章中，有时每幅图只使用一条线，因为这样可以更轻松地查看图变体之间的差异。

该图显示出很强的相关性：随着发动机尺寸的增大，燃油经济性也越来越差。还有一些有趣的离群值：一些具有大型发动机的汽车获得的燃油经济性高于平均水平。您认为它们是哪种汽车？

### 练习题

1.  您如何描述 `cty` 和 `hwy` 之间的关系？您是否对从该图得出结论有任何担忧？

2. `ggplot(mpg, aes(model, manufacturer)) + geom_point()` 会显示什么？它有用吗？您如何修改数据以使其更具参考价值？

```{r}
ggplot(mpg, aes(model, manufacturer)) +
  geom_point()
```

3.  描述以下每个图所使用的数据，美学映射和图层。您需要稍作猜测，因为您尚未看到所有数据集和函数，但请使用常识！在运行代码之前，请查看是否可以预测绘图的外观。

-   

```{r}
ggplot(mpg, aes(cty, hwy)) +
  geom_point()
```

-   

```{r}
ggplot(diamonds, aes(carat, price)) +
  geom_point()
```

-   

```{r}
ggplot(economics, aes(date, unemploy)) +
  geom_line()
```

-   

```{r}
ggplot(mpg, aes(cty)) +
  geom_histogram()
```

## 颜色，大小，形状和其他美学属性 {#aesthetics}

要向图表添加其他变量，我们可以使用其他美学元素，例如颜色，形状和大小（注意：尽管我在本书中都使用英式拼写，但 ggplot2 也接受美式拼写）。它们的工作方式与美学的 `x` 和 `y` 相同，并被添加到对 `aes()` 的调用中：\index{Aesthetics} \indexf{aes}

- `aes(displ, hwy, colour = class)` 
- `aes(displ, hwy, shape = drv)` 
- `aes(displ, hwy, size = cyl)` 

ggplot2将数据（例如，`f1`，`r`，`4`）转换为带有**标度**的美学对象（例如，`red`，`yellow`，`green`）的绘图。绘图中的每个绘图贴图都有一个标度。 The scale is also responsible for creating a guide, an axis or legend, that allows you to read the plot, converting aesthetic values back into data values. For now, we'll stick with the default scales provided by ggplot2. You'll learn how to override them in Chapter \@ref(scale-colour).

To learn more about those outlying variables in the previous
scatterplot, we could map the class variable to colour:

```{r qplot-aesthetics}
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point()
```

This gives each point a unique colour corresponding to its class. The
legend allows us to read data values from the colour, showing us that
the group of cars with unusually high fuel economy for their engine size
are two seaters: cars with big engines, but lightweight bodies.

If you want to set an aesthetic to a fixed value, without scaling it, do
so in the individual layer outside of `aes()` . Compare the following two
plots: \index{Aesthetics!setting}

 `r columns(2, 2/3)` 

```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(colour = "blue"))
ggplot(mpg, aes(displ, hwy)) +
  geom_point(colour = "blue")
```

In the first plot, the value "blue" is scaled to a pinkish colour, and a
legend is added. In the second plot, the points are given the R colour
blue. This is an important technique and you'll learn more about it in
小节 \@ref(setting-mapping). See `vignette("ggplot2-specs")` for the
values needed for colour and other aesthetics.

Different types of aesthetic attributes work better with different types
of variables. For example, colour and shape work well with categorical
variables, while size works well for continuous variables. The amount of
data also makes a difference: if there is a lot of data it can be hard
to distinguish different groups. An alternative solution is to use
faceting, as described next.

When using aesthetics in a plot, less is usually more. It's difficult to
see the simultaneous relationships among colour and shape and size, so
exercise restraint when using aesthetics. Instead of trying to make one
very complex plot that shows everything at once, see if you can create a
series of simple plots that tell a story, leading the reader from
ignorance to knowledge.

### Exercises

1.  Experiment with the colour, shape and size aesthetics. What happens
    when you map them to continuous values? What about categorical
    values? What happens when you use more than one aesthetic in a plot?

2.  What happens if you map a continuous variable to shape? Why? What
    happens if you map `trans` to shape? Why?

3.  How is drive train related to fuel economy? How is drive train
    related to engine size and class?

## Faceting {#qplot-faceting}

Another technique for displaying additional categorical variables on a
plot is faceting. Faceting creates tables of graphics by splitting the
data into subsets and displaying the same graph for each subset. You'll
learn more about faceting in 小节 \@ref(facet), but it's such a
useful technique that you need to know it right away. \index{Faceting}

There are two types of faceting: grid and wrapped. Wrapped is the most
useful, so we'll discuss it here, and you can learn about grid faceting
later. To facet a plot you simply add a faceting specification with
 `facet_wrap()` , which takes the name of a variable preceded by `~` .
\indexf{facet\_wrap}

 `r columns(1, 2 / 3, 1)`

```{r facet}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(~class)
```

You might wonder when to use faceting and when to use aesthetics. You'll
learn more about the relative advantages and disadvantages of each in
小节 \@ref(group-vs-facet).

### Exercises

1.  What happens if you try to facet by a continuous variable like
 `hwy` ? What about `cyl` ? What's the key difference?

2.  Use faceting to explore the 3-way relationship between fuel economy, 
    engine size, and number of cylinders. How does faceting by number of
    cylinders change your assessement of the relationship between engine
    size and fuel economy?

3.  Read the documentation for `facet_wrap()` . What arguments can you
    use to control how many rows and columns appear in the output?

4.  What does the `scales` argument to `facet_wrap()` do? When might you
    use it?

## Plot geoms {#plot-geoms}

You might guess that by substituting `geom_point()` for a different geom
function, you'd get a different type of plot. That's a great guess! In
the following sections, you'll learn about some of the other important
geoms provided in ggplot2. This isn't an exhaustive list, but should
cover the most commonly used plot types. You'll learn more in Chapters
\@ref(individual-geoms) and \@ref(collective-geoms).

- `geom_smooth()` fits a smoother to the data and displays the smooth
    and its standard error.

- `geom_boxplot()` produces a box-and-whisker plot to summarise the
    distribution of a set of points.

- `geom_histogram()` and `geom_freqpoly()` show the distribution of
    continuous variables.

- `geom_bar()` shows the distribution of categorical variables.

- `geom_path()` and `geom_line()` draw lines between the data points.
    A line plot is constrained to produce lines that travel from left to
    right, while paths can go in any direction. Lines are typically used
    to explore how things change over time.

### Adding a smoother to a plot {#smooth}

If you have a scatterplot with a lot of noise, it can be hard to see the
dominant pattern. In this case it's useful to add a smoothed line to the
plot with `geom_smooth()` : \index{Smoothing} \indexf{geom\_smooth}

 `r columns(1, 2/3)` 

```{r qplot-smooth}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth()
```

This overlays the scatterplot with a smooth curve, including an
assessment of uncertainty in the form of point-wise confidence intervals
shown in grey. If you're not interested in the confidence interval, turn
it off with `geom_smooth(se = FALSE)` .

An important argument to `geom_smooth()` is the `method` , which allows
you to choose which type of model is used to fit the smooth curve:

- `method = "loess"` , the default for small n, uses a smooth local
    regression (as described in `?loess` ). The wiggliness of the line is
    controlled by the `span` parameter, which ranges from 0 (exceedingly
    wiggly) to 1 (not so wiggly).

 `r columns(2, 2/3)` 

    ```{r smooth-loess, fig.align = "default"}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(span = 0.2)

ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(span = 1)
    ```

    Loess does not work well for large datasets (it's $O(n^2)$ in
    memory), so an alternative smoothing algorithm is used when $n$ is
    greater than 1, 000.

- `method = "gam"` fits a generalised additive model provided by the
**mgcv**package. You need to first load mgcv, then use a formula
    like `formula = y ~ s(x)` or `y ~ s(x, bs = "cs")` (for large data).
    This is what ggplot2 uses when there are more than 1, 000 points.
    \index{mgcv}

 `r columns(1, 2/3, 0.5)` 

    ```{r smooth-gam, message = FALSE, fig.align = "default"}
library(mgcv)
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x))
    ```

- `method = "lm"` fits a linear model, giving the line of best fit.

    ```{r smooth-lm, fig.align = "default"}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_smooth(method = "lm")
    ```

- `method = "rlm"` works like `lm()` , but uses a robust fitting
    algorithm so that outliers don't affect the fit as much. It's part
    of the**MASS**package, so remember to load that first.
    \index{MASS}

### Boxplots and jittered points {#boxplot}

When a set of data includes a categorical variable and one or more
continuous variables, you will probably be interested to know how the
values of the continuous variables vary with the levels of the
categorical variable. Say we're interested in seeing how fuel economy
varies within cars that have the same kind of drivetrain. We might start
with a scatterplot like this:

 `r columns(1, 2/3, 0.5)` 

```{r}
ggplot(mpg, aes(drv, hwy)) +
  geom_point()
```

Because there are few unique values of both `drv` and `hwy` , there is a
lot of overplotting. Many points are plotted in the same location, and
it's difficult to see the distribution. There are three useful
techniques that help alleviate the problem:

-   Jittering, `geom_jitter()` , adds a little random noise to the data
    which can help avoid overplotting. \index{Jittering}
    \indexf{geom\_jitter}

-   Boxplots, `geom_boxplot()` , summarise the shape of the distribution
    with a handful of summary statistics. \index{Boxplot}
    \indexf{geom\_boxplot}

-   Violin plots, `geom_violin()` , show a compact representation of the
    "density" of the distribution, highlighting the areas where more
    points are found. \index{Violin plot} \indexf{geom\_violin}

These are illustrated below:

 `r columns(3, 1)` 

```{r jitter-boxplot}
ggplot(mpg, aes(drv, hwy)) +
  geom_jitter()
ggplot(mpg, aes(drv, hwy)) +
  geom_boxplot()
ggplot(mpg, aes(drv, hwy)) +
  geom_violin()
```

Each method has its strengths and weaknesses. Boxplots summarise the
bulk of the distribution with only five numbers, while jittered plots
show every point but only work with relatively small datasets. Violin
plots give the richest display, but rely on the calculation of a density
estimate, which can be hard to interpret.

For jittered points, `geom_jitter()` offers the same control over
aesthetics as `geom_point()` : `size` , `colour` , and `shape` . For
 `geom_boxplot()` and `geom_violin()` , you can control the outline
 `colour` or the internal `fill` colour.

### Histograms and frequency polygons {#distribution}

Histograms and frequency polygons show the distribution of a single
numeric variable. They provide more information about the distribution
of a single group than boxplots do, at the expense of needing more
space. \index{Histogram} \indexf{geom\_histogram}

 `r columns(2, 2/3)` 

```{r dist}
ggplot(mpg, aes(hwy)) +
  geom_histogram()
ggplot(mpg, aes(hwy)) +
  geom_freqpoly()
```

Both histograms and frequency polygons work in the same way: they bin
the data, then count the number of observations in each bin. The only
difference is the display: histograms use bars and frequency polygons
use lines.

You can control the width of the bins with the `binwidth` argument (if
you don't want evenly spaced bins you can use the `breaks` argument). It
is**very important**to experiment with the bin width. The default just
splits your data into 30 bins, which is unlikely to be the best choice.
You should always try many bin widths, and you may find you need
multiple bin widths to tell the full story of your data.

```{r}
ggplot(mpg, aes(hwy)) +
  geom_freqpoly(binwidth = 2.5)
ggplot(mpg, aes(hwy)) +
  geom_freqpoly(binwidth = 1)
```

An alternative to the frequency polygon is the density plot, 
 `geom_density()` . I'm not a fan of density plots because they are harder
to interpret since the underlying computations are more complex. They
also make assumptions that are not true for all data, namely that the
underlying distribution is continuous, unbounded, and smooth.

To compare the distributions of different subgroups, you can map a
categorical variable to either fill (for `geom_histogram()` ) or colour
(for `geom_freqpoly()` ). It's easier to compare distributions using the
frequency polygon because the underlying perceptual task is easier. You
can also use faceting: this makes comparisons a little harder, but it's
easier to see the distribution of each group.

 `r columns(2, 1)` 

```{r dist-fill}
ggplot(mpg, aes(displ, colour = drv)) +
  geom_freqpoly(binwidth = 0.5)
ggplot(mpg, aes(displ, fill = drv)) +
  geom_histogram(binwidth = 0.5) +
  facet_wrap(~drv, ncol = 1)
```

### Bar charts {#bar}

The discrete analogue of the histogram is the bar chart, `geom_bar()` .
It's easy to use: \index{Barchart} \indexf{geom\_bar}

 `r columns(1, 1 / 2.5, 1)` 

```{r dist-bar}
ggplot(mpg, aes(manufacturer)) +
  geom_bar()
```

(You'll learn how to fix the labels in 小节 \@ref(theme-axis)).

Bar charts can be confusing because there are two rather different plots
that are both commonly called bar charts. The above form expects you to
have unsummarised data, and each observation contributes one unit to the
height of each bar. The other form of bar chart is used for
presummarised data. For example, you might have three drugs with their
average effect:

```{r}
drugs <- data.frame(
  drug = c("a", "b", "c"),
  effect = c(4.2, 9.7, 6.1)
)
```

To display this sort of data, you need to tell `geom_bar()` to not run
the default stat which bins and counts the data. However, I think it's
even better to use `geom_point()` because points take up less space than
bars, and don't require that the y axis includes 0.

 `r columns(2, 2/3)` 

```{r}
ggplot(drugs, aes(drug, effect)) +
  geom_bar(stat = "identity")
ggplot(drugs, aes(drug, effect)) +
  geom_point()
```

### Time series with line and path plots {#line}

Line and path plots are typically used for time series data. Line plots
join the points from left to right, while path plots join them in the
order that they appear in the dataset (in other words, a line plot is a
path plot of the data sorted by x value). Line plots usually have time
on the x-axis, showing how a single variable has changed over time. Path
plots show how two variables have simultaneously changed over time, with
time encoded in the way that observations are connected.

Because the year variable in the mpg dataset only has two values, 
we'll show some time series plots using the `economics` dataset, which
contains economic data on the US measured over the last 40 years. The
figure below shows two plots of unemployment over time, both produced
using `geom_line()` . The first shows the unemployment rate while the
second shows the median number of weeks unemployed. We can already see
some differences in these two variables, particularly in the last peak, 
where the unemployment percentage is lower than it was in the preceding
peaks, but the length of unemployment is high. \indexf{geom\_line}
\indexf{geom\_path} \index{Data!economics@\texttt{economics}}

 `r columns(2, 2.4 / 4)` 

```{r line-employment}
ggplot(economics, aes(date, unemploy / pop)) +
  geom_line()
ggplot(economics, aes(date, uempmed)) +
  geom_line()
```

To examine this relationship in greater detail, we would like to draw
both time series on the same plot. We could draw a scatterplot of
unemployment rate vs. length of unemployment, but then we could no
longer see the evolution over time. The solution is to join points
adjacent in time with line segments, forming a *path* plot.

Below we plot unemployment rate vs. length of unemployment and join the
individual observations with a path. Because of the many line crossings, 
the direction in which time flows isn't easy to see in the first plot.
In the second plot, we colour the points to make it easier to see the
direction of time.

```{r path-employ}
ggplot(economics, aes(unemploy / pop, uempmed)) +
  geom_path() +
  geom_point()

year <- function(x) as.POSIXlt(x)$year + 1900
ggplot(economics, aes(unemploy / pop, uempmed)) +
  geom_path(colour = "grey50") +
  geom_point(aes(colour = year(date)))
```

We can see that unemployment rate and length of unemployment are highly
correlated, but in recent years the length of unemployment has been
increasing relative to the unemployment rate.

With longitudinal data, you often want to display multiple time series
on each plot, each series representing one individual. To do this you
need to map the `group` aesthetic to a variable encoding the group
membership of each observation. This is explained in more depth in
Chapter \@ref(collective-geoms).
\index{Longitudinal data|see{Data, longitudinal}}
\index{Data!longitudinal}

### Exercises

1.  What's the problem with the plot created by
 `ggplot(mpg, aes(cty, hwy)) + geom_point()` ? Which of the geoms
    described above is most effective at remedying the problem?

2.  One challenge with `ggplot(mpg, aes(class, hwy)) + geom_boxplot()` 
    is that the ordering of `class` is alphabetical, which is not
    terribly useful. How could you change the factor levels to be more
    informative?

    Rather than reordering the factor by hand, you can do it
    automatically based on the data:
 `ggplot(mpg, aes(reorder(class, hwy), hwy)) + geom_boxplot()` . What
    does `reorder()` do? Read the documentation.

3.  Explore the distribution of the carat variable in the `diamonds` 
    dataset. What binwidth reveals the most interesting patterns?

4.  Explore the distribution of the price variable in the `diamonds` 
    data. How does the distribution vary by cut?

5.  You now know (at least) three ways to compare the distributions of
    subgroups: `geom_violin()` , `geom_freqpoly()` and the colour
    aesthetic, or `geom_histogram()` and faceting. What are the
    strengths and weaknesses of each approach? What other approaches
    could you try?

6.  Read the documentation for `geom_bar()` . What does the `weight` 
    aesthetic do?

7.  Using the techniques already discussed in this chapter, come up with
    three ways to visualise a 2d categorical distribution. Try them out
    by visualising the distribution of `model` and `manufacturer` , 
 `trans` and `class` , and `cyl` and `trans` .

## Modifying the axes {#axes}

You'll learn the full range of options available in later chapters, but
two families of useful helpers let you make the most common
modifications. `xlab()` and `ylab()` modify the x- and y-axis labels:
\indexf{xlab} \indexf{ylab}

 `r columns(3, 1)` 

```{r}
ggplot(mpg, aes(cty, hwy)) +
  geom_point(alpha = 1 / 3)

ggplot(mpg, aes(cty, hwy)) +
  geom_point(alpha = 1 / 3) +
  xlab("city driving (mpg)") +
  ylab("highway driving (mpg)")

# Remove the axis labels with NULL
ggplot(mpg, aes(cty, hwy)) +
  geom_point(alpha = 1 / 3) +
  xlab(NULL) +
  ylab(NULL)
```

 `xlim()` and `ylim()` modify the limits of axes: \indexf{xlim}
\indexf{ylim}

```{r}
ggplot(mpg, aes(drv, hwy)) +
  geom_jitter(width = 0.25)

ggplot(mpg, aes(drv, hwy)) +
  geom_jitter(width = 0.25) +
  xlim("f", "r") +
  ylim(20, 30)

# For continuous scales, use NA to set only one limit
ggplot(mpg, aes(drv, hwy)) +
  geom_jitter(width = 0.25, na.rm = TRUE) +
  ylim(NA, 30)
```

Changing the axes limits sets values outside the range to `NA` . You can
suppress the associated warning with `na.rm = TRUE` , but be careful. If
your plot calculates summary statistics (e.g., sample mean), this
conversion to `NA` occurs *before* the summary statistics are computed, 
and may lead to undesirable results in some situations.

## Output {#output}

Most of the time you create a plot object and immediately plot it, but
you can also save a plot to a variable and manipulate it:

```{r variable}
p <- ggplot(mpg, aes(displ, hwy, colour = factor(cyl))) +
  geom_point()
```

Once you have a plot object, there are a few things you can do with it:

-   Render it on screen with `print()` . This happens automatically when
    running interactively, but inside a loop or function, you'll need to
 `print()` it yourself. \indexf{print}

 `r columns(1, 1 / 2)` 

    ```{r}
print(p)
    ```

-   Save it to disk with `ggsave()` , described in 小节 \@ref(saving).

    ```{r, eval = FALSE}
# Save png to disk
ggsave("plot.png", p, width = 5, height = 5)
    ```

-   Briefly describe its structure with `summary()` . \indexf{summary}

    ```{r}
summary(p)
    ```

-   Save a cached copy of it to disk, with `saveRDS()` . This saves a
    complete copy of the plot object, so you can easily re-create it
    with `readRDS()` . \indexf{saveRDS} \indexf{readRDS}

    ```{r summary}
saveRDS(p, "plot.rds")
q <- readRDS("plot.rds")
    ```

```{r, include = FALSE}
unlink("plot.png")
unlink("plot.rds")
```

You'll learn more about how to manipulate these objects in Chapter
\@ref(programming).
